Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
Add files via upload

We define the \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them. The \textit{neighborhood} of a node $u$ with radius $r$ is the set of nodes such that they are at distance no greater than $r$ from $u$ and it is denoted by $N_r(u)$ and $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$. The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
\textit{neighborhood} with radius $r$ of $u$ and the relative edges with endpoints in $N_r(u)$. The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
\subsection{The neighborhood subgraph pairwise distance kernel}
In this section, we briefly desbribe an efficient kernel named NSPDK \cite{nspdk} which allows to measure the similarity between labeled graphs. NSPDK is an instance of decompositional kernel \cite{convolution-kernel}.

@@

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to use node labeling fuctions $L$ that take into account node degrees for their labels such that $\ell(u) = \ell(v)$ if $|d(u) - d(v)|\leq \lambda$, in which $\lambda$ is a hyper parameter. It is due to the assumption that nodes with similar degrees tend to share common properties. The values of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propse a method which model the context of two nodes to represent for link connecting them.

@@

\textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on training set in which we use one fold for training and the rest two folds for validation. We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ for node degree function in $\lbrace 1, 2 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively. Finally, the regularization tradeoff $C$ for the SVM is picked up in $\lbrace 10^{-4}, 10^{-3}, 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2, 10^3,\ 10^4 \rbrace$.

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively.

\begin{table}
\caption{The performance in percentage on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores. }
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|}

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.

>>>>

We define the \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them. The \textit{neighborhood} of a node $u$ with radius $r$ is the set of nodes such that they are at distance no greater than $r$ from $u$ and it is denoted by $N_r(u)$ and $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$. The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
\textit{neighborhood} with radius $r$ of $u$ and the relative edges with endpoints in $N_r(u)$. The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$. We also notate the maximum node degree in the graph $G$ as $d(G)$, $d(G) = max\lbrace d(u)\ |\ u \in V \rbrace$
\subsection{The neighborhood subgraph pairwise distance kernel}
In this section, we briefly desbribe an efficient kernel named NSPDK \cite{nspdk} which allows to measure the similarity between labeled graphs. NSPDK is an instance of decompositional kernel \cite{convolution-kernel}.

@@

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to a node labeling fuction $\ell$ such that nodes with similar degrees are assigned the same label. It is due to the assumption that nodes with similar degrees tend to share common properties. Following is the definition of the the function:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		6+i,\ & \mbox{if }  5 + \frac{d(G) - 5}{\lambda-5}*i \leq d(u) < 5 + \frac{d(G) - 5}{\lambda-5}*(i+1)
	\end{array}
\right.$,
\end{center}
where $\lambda > 5$ is the number of labels used to label for nodes in the graphs. The values of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propse a method which model the context of two nodes to represent for link connecting them.

@@

\textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on training set in which we use one fold for training and the rest two folds for validation. We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ in node label function in $\lbrace 10, 15 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively. Finally, the regularization tradeoff $C$ for the SVM is picked up in $\lbrace 10^{-4}, 10^{-3}, 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2, 10^3,\ 10^4 \rbrace$.

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively.

\begin{table}
\caption{The ROC-AUC performance on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores. }
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|}

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
	& ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$)\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.
